Neural Sparse Gaussian Process: For Updated Exploration

### 2023-04-14 paper/main.tex
added abstract
Minor

%\title{Investigatin Uncertainty Quantification in Model-based Reinforcement Learning}
% \title{Model-based Reinforcement Learning with Fast Posterior Updates}
\title{Neural Sparse Gaussian Process: For Updated Exploration}
\author{%
  Aidan ~Scannell \\
  Aalto University\\
  %Finnish Center for Artificial Intelligence \\
  \texttt{aidan.scannell@aalto.fi}
  \And
  Paul ~Chang \\
  Aalto University\\
  \texttt{paul.chang@aalto.fi}
  \And
  Ella ~Tamir \\
  Aalto University\\
  \texttt{ella.tamir@aalto.fi}
  \And
  Arno ~Solin \\
  Aalto University\\
  \texttt{arno.solin@aalto.fi}
  \And
  Joni ~Pajarinen \\
  Aalto University\\
  \texttt{joni.pajarinen@aalto.fi}
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

% Bibliography
\usepackage[maxcitenames=1, maxbibnames=4, doi=false, isbn=false, eprint=true, backend=bibtex, hyperref=true, url=false, style=authoryear-comp]{biblatex}
\addbibresource{zotero-library.bib}
% \addbibresource{paper/zotero-library.bib}

@@

\section{Background} \label{sec:background}
% \section{dual SVGP}
% In this section we extend these fast updates to environment's with high dimensional state spaces and large data sets.
% % Our method draws on the connection between BNNs and GPs and formulates a function space SVGP posterior given
% Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
% \parencite{khanApproximate2019} to formulate a function space SVGP posterior,
% where we can apply the fast updates from \cref{eq-dual-update-svgp}.
% At a high-level, we first use Laplace's approximation to obtain a weight space posterior for our BNN.
% We then linearise our BNN around the optimal parameters and interpret it as a GP.
% Finally, we formulate a lower rank approximation of this GP posterior (i.e. a SVGP posterior) using inducing variables.
% % formulates a function space SVGP posterior by drawing on the connection between BNNs and GPs.

@@

\section*{Acknowledgements}
Aidan Scannell is funded by the Finnish Center for Artificial Intelligence.

% \section*{References}
\small
\printbibliography
\normalsize
% TODO make bibliography small a better way

References follow the acknowledgments. Use unnumbered first-level heading for
the references. Any choice of citation style is acceptable as long as you are
consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
when listing the references.
Note that the Reference section does not count towards the page limit.
\medskip

>>>>

%\title{Investigatin Uncertainty Quantification in Model-based Reinforcement Learning}
% \title{Model-based Reinforcement Learning with Fast Posterior Updates}
%\title{Sequential Decision-Making under Uncertainty with Big Data}
\title{Neural Sparse Gaussian Process: For Updated Exploration}

\author{%
  Aidan ~Scannell \\
  Aalto University\\
  %Finnish Center for Artificial Intelligence \\
  \texttt{aidan.scannell@aalto.fi}
  \And
  Paul ~Chang \\
  Aalto University\\
  \texttt{paul.chang@aalto.fi}
  \And
  Ella ~Tamir \\
  Aalto University\\
  \texttt{ella.tamir@aalto.fi}
  \And
  Arno ~Solin \\
  Aalto University\\
  \texttt{arno.solin@aalto.fi}
  \And
  Joni ~Pajarinen \\
  Aalto University\\
  \texttt{joni.pajarinen@aalto.fi}
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

% Bibliography
%\usepackage[maxcitenames=1, maxbibnames=4, doi=false, isbn=false, eprint=true, backend=bibtex, hyperref=true, url=false, style=authoryear-comp]{biblatex}
%\addbibresource{zotero-library.bib}
% \addbibresource{paper/zotero-library.bib}

@@

\section{Background} \label{sec:background}

\cite{hernandez2016scalable}
% \section{dual SVGP}
% In this section we extend these fast updates to environment's with high dimensional state spaces and large data sets.
% % Our method draws on the connection between BNNs and GPs and formulates a function space SVGP posterior given
% Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
% \parencite{khanApproximate2019} to formulate a function space SVGP posterior,
% where we can apply the fast updates from \cref{eq-dual-update-svgp}.
% At a high-level, we first use Laplace's approximation to obtain a weight space posterior for our BNN.
% We then linearise our BNN around the optimal parameters and interpret it as a GP.
% Finally, we formulate a lower rank approximation of this GP posterior (i.e. a SVGP posterior) using inducing variables.
% % formulates a function space SVGP posterior by drawing on the connection between BNNs and GPs.

@@

\begin{ack}
ASK A ABOUT THIS SECTION:
Aidan Scannell is funded by the Finnish Center for Artificial Intelligence.
\end{ack}

% \section*{References}
%\small
%\printbibliography
%\normalsize
% TODO make bibliography small a better way

%References follow the acknowledgments. Use unnumbered first-level heading for
%the references. Any choice of citation style is acceptable as long as you are
%consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
%when listing the references.
%Note that the Reference section does not count towards the page limit.
%\medskip

\phantomsection%
\addcontentsline{toc}{section}{References}
\begingroup
\small
\bibliographystyle{abbrvnat}
\bibliography{main-blx,zotero-library,bibliography}
\endgroup

\clearpage
